Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
updated abstract

\begin{abstract}
%\todo[inline]{Topics and LDA sooner, Topics/concept location is a known
%  research area and we're saying they don't do enough}

% Maybe specify the hard work we did annotating the data

% our field
%  Within the field of mining software repositories, a
To understand the latent subject matter of software development artifacts, researchers have proposed topic modeling and concept location.
%These techniques rely on the automated application of machine learning algorithms to corpora.
These techniques use unsupervised machine learning algorithms find topics or concepts.
% the problem
These topics are word-lists lacking semantic interpretation, which are difficult to distinguish and interpret. 
%Results are usually abstract, as the topics that are automatically extracted 
% the solution 
In order to have a meaningful discussion about the topics of software development, we must be able to attach meaningful labels to these topics. 
%However, current software engineering topic analysis and concept analysis research relies on manual naming and labelling of topics.
% the labelling research
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
% a sub problem
% While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
% what we do

To solve this problem, this paper introduces \emph{labelled topic extraction}, 
in which topics are extracted from commit comments and given labels relating to a cross-project taxonomy. 
% data mining generalizable
Our approach is 
%To ensure we have a 
generalizable and project-agnostic, as we label topics using non-functional requirements,
% these qualities 
which apply across software systems.% and their development artifacts.
% We used real world data
We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. 
% We used LDA, CVS, Bitkeeper
We extracted topics using Latent Dirichlet Allocation (LDA) from the commit-log comments of their source control systems (CVS and BitKeeper). 
% We show NFRs exist
%Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, 
%and we identified topic trends over time. 	
% we can label stuff
Our labelled topic extraction technique produces appropriate, context-sensitive labels relevant to these projects, providing fresh insight into their evolving software development activities.
\end{abstract}

>>>>

\begin{abstract}
% %\todo[inline]{Topics and LDA sooner, Topics/concept location is a known
% %  research area and we're saying they don't do enough}

% % Maybe specify the hard work we did annotating the data

% % our field
% %  Within the field of mining software repositories, a
% To understand the latent subject matter of software development artifacts, researchers have proposed topic modeling and concept location.
% %These techniques rely on the automated application of machine learning algorithms to corpora.
% These techniques use unsupervised machine learning algorithms find topics or concepts.
% % the problem
% These topics are word-lists lacking semantic interpretation, which are difficult to distinguish and interpret. 
% %Results are usually abstract, as the topics that are automatically extracted 
% % the solution 
% In order to have a meaningful discussion about the topics of software development, we must be able to attach meaningful labels to these topics. 
% %However, current software engineering topic analysis and concept analysis research relies on manual naming and labelling of topics.
% % the labelling research
% Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
% % a sub problem
% % While too much specificity can produce non-generalizable results, too little produces broad learners that do not provide much immediately useful detail. 
% % what we do

% To solve this problem, this paper introduces \emph{labelled topic extraction}, 
% in which topics are extracted from commit comments and given labels relating to a cross-project taxonomy. 
% % data mining generalizable
% Our approach is 
% %To ensure we have a 
% generalizable and project-agnostic, as we label topics using non-functional requirements,
% % these qualities 
% which apply across software systems.% and their development artifacts.
% % We used real world data
% We evaluated our approach with an experimental study on two large-scale database projects, MySQL and MaxDB. 
% % We used LDA, CVS, Bitkeeper
% We extracted topics using Latent Dirichlet Allocation (LDA) from the commit-log comments of their source control systems (CVS and BitKeeper). 
% % We show NFRs exist
% %Our results were generalizable across the two projects, showing that non-functional requirements were commonly discussed, 
% %and we identified topic trends over time. 	
% % we can label stuff
% Our labelled topic extraction technique produces appropriate, context-sensitive labels relevant to these projects, providing fresh insight into their evolving software development activities.

Researchers have used topic modeling and concept location to understand the latent topics of software development artifacts.
These techniques use unsupervised machine-learning algorithms recover topics.
These topics are word-lists and are difficult to distinguish and interpret. 
Topics are not meaningful until they have been named or interpreted.
Current topic labelling approaches are manual, and do not use domain-specific knowledge to improve, contextualize, or describe results for the developers.
We propose a solution: \emph{labelled topic extraction}.
Topics are extracted using Latent Dirichlet Allocation (LDA) from commit-log comments extracted from source control systems such as CVS and BitKeeper. 
Then these topics given labels relating to a generalizable cross-project taxonomy consisting of non-functional requirements (NFRs).
Our approach was evaluated  with experiments and case studies on two large-scale RDBMS projects: MySQl and MaxDB.
Labelled topic extraction produces appropriate, context-sensitive labels relevant to these projects, which provides fresh insight into their evolving software development activities.

\end{abstract}
